Serpe SC data

### 2025-01-30 SerpeSCdata.Rmd
final SC function addition

@@

plot.serpe = function(gene.name){
serpe.annotated.gene = data.frame(level = as.numeric(serpe[gene.name,]),
                                  cluster = serpe.annotated.names,
                                  color = "darkgreen")

par(mar = c(4, 13, 4, 8))
barplot(as.numeric(serpe.all[,"level"])-1,
        names.arg = serpe.all$cluster,
        las = 2, 
        beside = T,
        col = serpe.all$color,
        cex.names = .75,
        main = gene.name,
        horiz = T,
        xlab = "Mean Expression Level per Cell")
      legend(x = max(as.numeric(serpe.all[,"level"])-1),
             y = 125,
             pch = 21,
             legend = c("Glia", "Interneurons", "Motor Neurons", "Manually Curated"),
             pt.bg = c("steelblue", "gold", "brown", "darkgreen"),
             bty = "n",
             xpd = T,
             pt.cex = 1.5,
             y.intersp = 1)
}
```

```{r echo = F, fig.width= 10, fig.height=15}

##gene.name = "gbb"

##plot.serpe(gene.name)

@@

  #serpe.all$level = serpe.all$level - 1

  #highlight = rep(0, nrow(serpe.all))
  #highlight[(serpe.all$level > highlight.cutoff*(mean(serpe.all$level)))] = 1
  #serpe.all$highlight = serpe.all$level * highlight

  #serpe.all$color[highlight > 0 & serpe.all$color == "lightgreen"] = "darkgreen"
  #serpe.all$color[highlight > 0 & serpe.all$color == "thistle1"] = "brown"
  #serpe.all$color[highlight > 0 & serpe.all$color == "lightyellow"] = "gold"
  #serpe.all$color[highlight > 0 & serpe.all$color == "lightcyan"] = "royalblue"
  serpe.all$color[serpe.all$level < 1.5] = "darkgrey"

  #label.colors = serpe.all$color

  #label.colors[serpe.all$color == "darkgreen"] = "darkgreen"
  #label.colors[serpe.all$color == "brown"] = "brown"
  #label.colors[serpe.all$color == "gold"] = "gold"
  #label.colors[serpe.all$color == "royalblue"] = "royalblue"
  #serpe.all$label.colors = label.colors

@@

gene.name = "put"

@@

>>>>

library(gplots)

@@

@@

  serpe.all$color[serpe.all$level < 1.5] = "darkgrey"

@@

gene.name = "burs"

@@

```{r echo = F, fig.width=16, fig.height=10}

heat.genes = c("dpp", "gbb", "put", "wit", "mav", "sax", "tkv", "repo", "ACC", "Ack-like")

serpe.heatmap = function(heat.genes){
heat.data = na.omit(cbind(serpe[heat.genes,],
                          cbind(serpe.mn[heat.genes,],
                                cbind(serpe.inter[heat.genes,], serpe.glia[heat.genes,]))))

heat.data = apply(heat.data, MARGIN = 2, as.numeric)
#heat.data = log2(heat.data)
row.names(heat.data) = heat.genes

#heat.data[heat.data == 0] = NA

Cluster.id = c(serpe.annotated.names,
               colnames(serpe.mn),
               colnames(serpe.inter),
               serpe.glia.names)

Cluster.labelcolor = c(rep("darkgreen", length(serpe.annotated.names)),
                       rep("brown", ncol(serpe.mn)),
                       rep("orange", ncol(serpe.inter)),
                       rep("steelblue", length(serpe.glia.names)))

heat.colors = colorRampPalette(c("grey95", "steelblue", "gold", "red3"))

numcols = 100

max.break = log2(max(heat.data))

if(max.break > 7){
  max.break = 7
}

color.breaks = 2^(c(0:(numcols))*(max.break/(numcols + 1)))

heatmap.2(heat.data,
        Colv = NA,
        #Rowv = NA,
        labCol = Cluster.id,
        scale = 'none',
        ColSideColors = Cluster.labelcolor,
        trace = "none",
        col = heat.colors(numcols),
        dendrogram = "none",
        na.color = "white",
        key.title = "Mean Expression",
        colCol = Cluster.labelcolor,
        margins = c(10, 5), 
        colsep = c(18, 46, 95),
        sepcolor = "black",
        breaks = color.breaks)
legend("left",
       title = "Cell Types",
       legend = c("Manually Currated", "Motor Neurons", "Interneurons", "Glia"),
       fill = c("darkgreen", "brown", "orange", "steelblue"),
       xpd = T)

#library(corrplot)
#corrplot(heat.data, is.corr = F, col =COL2("RdBu", 200))

```{r echo = F, fig.width=16, fig.height=10}

heat.genes = c("dpp", "gbb", "put", "wit", "mav", "sax", "tkv", "repo", "ACC", "Ack-like")##, "trio")#, "Rac1")

heat.data = na.omit(cbind(serpe.mn[heat.genes,],
                          cbind(serpe.inter[heat.genes,], serpe.glia[heat.genes,])))

heat.data = apply(heat.data, MARGIN = 2, as.numeric)
#heat.data = log2(heat.data)
row.names(heat.data) = heat.genes

#heat.data[heat.data == 0] = NA

Cluster.id = c(colnames(serpe.mn),
               colnames(serpe.inter),
               serpe.glia.names)

Cluster.labelcolor = c(rep("brown", ncol(serpe.mn)),
                       rep("orange", ncol(serpe.inter)),
                       rep("steelblue", length(serpe.glia.names)))

heat.colors = colorRampPalette(c("grey95", "steelblue", "gold", "red3"))

numcols = 100

max.break = log2(max(heat.data))

if(max.break > 7){
  max.break = 7
}

color.breaks = 2^(c(0:(numcols))*(max.break/(numcols + 1)))

heatmap.2(heat.data,
        Colv = NA,
        #Rowv = NA,
        labCol = Cluster.id,
        scale = 'none',
        ColSideColors = Cluster.labelcolor,
        trace = "none",
        col = heat.colors(numcols),
        dendrogram = "none",
        na.color = "white",
        key.title = "Mean Expression",
        colCol = Cluster.labelcolor,
        margins = c(10, 5), 
        colsep = c(28, 77),
        sepcolor = "black",
        breaks = color.breaks)
legend("left",
       title = "Cell Types",
       legend = c("Motor Neurons", "Interneurons", "Glia"),
       fill = c("brown", "orange", "steelblue"),
       xpd = T)
#library(corrplot)
#corrplot(heat.data, is.corr = F, col =COL2("RdBu", 200))

```{r echo = F, fig.width=16, fig.height=10}

heat.genes = c("dpp", "gbb", "put", "wit", "mav", "sax", "tkv", "repo", "ACC", "Ack-like")

heat.data = na.omit(serpe[heat.genes,])

heat.data = apply(heat.data, MARGIN = 2, as.numeric)
#heat.data = log2(heat.data)
row.names(heat.data) = heat.genes

#heat.data[heat.data == 0] = NA

Cluster.id = c(serpe.annotated.names)

Cluster.labelcolor = c(rep("darkgreen", length(serpe.annotated.names)))

heat.colors = colorRampPalette(c("grey95", "steelblue", "gold", "red3"))

numcols = 100

max.break = log2(max(heat.data))

if(max.break > 7){
  max.break = 7
}

color.breaks = 2^(c(0:(numcols))*(max.break/(numcols + 1)))

heatmap.2(heat.data,
        Colv = NA,
        #Rowv = NA,
        labCol = Cluster.id,
        scale = 'none',
        ColSideColors = Cluster.labelcolor,
        trace = "none",
        col = heat.colors(numcols),
        dendrogram = "none",
        na.color = "white",
        key.title = "Mean Expression",
        colCol = Cluster.labelcolor,
        margins = c(10, 5), 
        #colsep = c(18, 46, 95),
        #sepcolor = "black",
        breaks = color.breaks)
legend("left",
       title = "Cell Types",
       legend = c("Manually Currated"),
       fill = c("darkgreen"),
       xpd = T)
#library(corrplot)
#corrplot(heat.data, is.corr = F, col =COL2("RdBu", 200))
